\section{Introduction}
The world has become more connected over the past decades thanks to the networked nature of the technologies of the day. It is seldom possible to spend a whole day without single interaction on the Internet. The Internet gives platforms where we can not only connect with our social counterparts but also exchange ideas and express opinions. These new mediums have become so ubiquitous, that some research suggests that they might be affecting our broader psychological state \cite{d20122}. But on the positive side, studies have also proposed different ways in which this medium could be used for measuring and intervening in the matters of mental health\cite{DeChoudhury2016,DeChoudhury2014} 
One aspect of this is measuring signals and patterns in the data that are predictors of certain distresses. A good example\cite{DeChoudhury2014,DeChoudhury2016} looked at statistical relations of mental health and depression community with suicidal ideation. In their work, the authors explore linguistic and social characteristics that evaluate user's propensity to suicidal ideation. 
Another crucial and related work was carried out by \cite{gkotsis2017characterisation}, where they characterized mental health related posts on sub-reddit, and developed models to accurately predict type of condition based of informed language models.

In most cases, the work aimed at measuring signals of distress and not support, which is the complimentary part of the process and which make these on-line communities work. The only reason for expression of distress was because the users expect support from the community. In this work we measure the phenomenon of social support in online communities that deal with suicidal thoughts and suicidal expressions. We do this by a data driven study of Suicide Watch sub-reddit and baseline it using a large random collection of reddit threads from the Front page of the Reddit website. We in the process of measuring, try to ope rationalize a well establish theory on off-line support from literature \cite{minkler2005improving} using network topology and content features and show that the measures developed off-line hold true for this particular supportive community

%% SV: to add: condense the pubchline and the main methods and contributions. 5 main steps - network structure would be the typical network analysis which actually doesn't show anything in these datasets, but with the subsequent methods proposed here, significant differences are shown, and they provide a means to systematically analyze these types of communities